StreamReduce: Processing Data Streams\\and Avoiding Work

### 2012-05-05 paper/paper.tex
Add acknowledgements section

>>>>

\subsection*{Acknowledgments}
I would like to acknowledge Martin Rinard for giving me direction for my initial idea
and guiding me to apply the data stream model to StreamReduce; Sasa Misailovic for being
a sounding board for ideas and providing me with background research; Daniel Erenrich for
providing information about data stream management systems; and SIPB for providing the
XVM service, which made deploying a StreamReduce cluster painless.
